---
title: "MiRAE: Minimal Reproducible Analysis Example"
output: github_document
---


```{r setup, include=FALSE}
library(here)
library(fs)
```

## Purpose

This repository contains code for a Minimal Reproducible Analysis Example (MiRAE). This was developed as a minimal example of what an R project compliant to the PPS data management plan should look like.

## Project Structure

details to be added...

```{r, echo = FALSE}
fs::dir_tree(here("."))
```

## Try it yourself

Please download the project and poke around ! It is very simple to do so.

You simply need to have __Git__ installed on your computer. You can do that manually (https://git-scm.com/downloads) or via the WUR available software interface.

Just click on the green button above __"Clone or download"__ and copy the repo url, then...

### Using Rstudio

* Go to File > New Project... > Version Control > Git, then paste the repo url in the field _Repository url:_.
* Tell Rstudio where you want the project to be clone on our computer in _Project directory name:_.
* When you are ready just click on __Create Project__ and the project will be automatically downloaded on your computer and open in an RStudio session. 


### Using Git directly

Go to the location where you want to clone the project, then right click on a blank area and select _Git Bash Here_.
A Bash terminal will open. Then type:

```{bash, eval=FALSE}
git clone https://github.com/ALanguillaume/MiRAE.git
```





